---
title: "Analysis of the Armenian Pub Survey Data in R Markdown"
author: "Brian Buonauro"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

The purpose of this analysis is to provide a demonstration of linear regression, plotting, and cleaning of survey data in R, presented in R Markdown.

## Loading the Packages

The only package used for this analysis was tidyverse.

```{r packages}
library(tidyverse)
```

## Loading the Dataset

```{r dataset, include=FALSE}
data <- read.csv("C:/DIRECTORY/armenian_pubs.csv")
options(scipen = 999)
```

Data was sourced from a [Kaggle](https://www.kaggle.com/datasets/erikhambardzumyan/pubs) user @ErikHambardzumyan and was collected during late February and early March of 2017 from 175 people in Armenia regarding their habits around going to pubs.

## Cleaning the Dataset

The unique() function was used on all columns to observe differences in responses and formulate a plan for cleaning the dataset. The following columns were found to need minor cleaning to make the data easier to understand and draw conclusions from: X.Occupation, Fav_Pub, Lifestyle, and Occasions.

------------------------------------------------------------------------

```{r cleaning_1}
data$X.Occupation <- trimws(data$X.Occupation)
```

The X.Occupation column only needed trailing whitespace trimmed.

------------------------------------------------------------------------

```{r cleaning_2}
data$Fav_Pub <- trimws(data$Fav_Pub)
data$Fav_Pub[data$Fav_Pub == "BullDog"] <- "Bulldog"
data$Fav_Pub[data$Fav_Pub == "Do not have one"] <- NA
data$Fav_Pub[data$Fav_Pub == "I don't like pubs"] <- NA
data$Fav_Pub[data$Fav_Pub == "I have none"] <- NA
data$Fav_Pub[data$Fav_Pub == "37 pub"] <- "Pub 37"
data$Fav_Pub[data$Fav_Pub == "Tom collins"] <- "Tom Collins"
data$Fav_Pub[data$Fav_Pub == "Void"] <- NA
data$Fav_Pub[data$Fav_Pub == "VOID"] <- NA
```

The Fav_Pub column needed trailing whitespace trimmed, duplicates merged, and string values indicating the respondent had no opinion switched to a value of NA.

------------------------------------------------------------------------

```{r cleaning_3}
data$Lifestyle <- trimws(data$Lifestyle)
data$Lifestyle[data$Lifestyle == "Busy(student life, work)"] <- "Student"
data$Lifestyle[data$Lifestyle == "Sport, art, traveling"] <- "Sport"
data$Lifestyle[data$Lifestyle == "Adventure/traveling/exploring"] <- "Travel"
data$Lifestyle[data$Lifestyle == "Rock, punk"] <- "Music"
data$Lifestyle[data$Lifestyle == "Business, sports, dance"] <- "Business"
```

The Lifestyle column needed trailing whitespace trimmed and answers simplified to the primary response.

------------------------------------------------------------------------

```{r}
data$Occasions <- trimws(data$Occasions)
data$Occasions[data$Occasions == "Never"] <- NA
data$Occasions[data$Occasions == "Nowere"] <- NA
data$Occasions[data$Occasions == "For listening  good music"] <- "For listening to good music"
data$Occasions[data$Occasions == "Birthdays"] <- "Special events/parties"
data$Occasions[data$Occasions == "chem aycelum"] <- "I'm thirsty"
```

The Occasions column needed whitespace trimmed, duplicates merged, string values indicating the respondent had no opinion switched to a value of NA, and a value needed to be translated to English. The string value "chem aycelum" (transliterated to ծհեմ այծելuմ in the Armenian alphabet) roughly translates to "I'm thirsty" in English from Armenian per an online search.

------------------------------------------------------------------------

## Table Statistics & Plots

```{r summary}
summary(data)
```

```{r plots_1}
data %>% ggplot() + geom_col(aes(x = Freq, y = frequency(Freq), fill = Occasions)) +
  labs(title = "How Often Do You Go to the Pub?", 
       x = "Frequency", y = "Number of Responses")
```

Observations:

-   To "Hang out with friends" was the only response for respondents who also answered that they frequent pubs several times per week.

-   Responses of "For listening to good music", "I'm thirsty", and "Special events/parties" were most prevalent reasons for visiting pubs among respondents who answered that they rarely go to pubs.

```{r plots_2}
data %>% ggplot() + geom_col(aes(x = Freq, y = frequency(Freq), fill = Lifestyle)) +
  labs(title = "How Often Do You Go to the Pub?", 
       x = "Frequency", y = "Number of Responses")
```

Observations:

-   Respondents who answered "Nightlife" to a question about their lifestyle were likely to frequent pubs more than just rarely.

-   Respondents who answered "Sport" to a question about their lifestyle were less likely to frequent pubs.

```{r plots_3}
data %>% ggplot() + geom_point(aes(x = WTS, y = Age., alpha = Income.)) +
  labs(title = "How Much Do You Spend at the Pub? (in Armenian Drams)", 
       x = "Willing to Spend Per Visit", y = "Age")
```

Observations:

-   Older and wealthier respondents appear to have more reserved spending habits.

-   Most respondents are young and spend 10,000 Dram (\~\$25 USD) or less on a trip to the pub.

-   Young and low income appear to be over-sampled in this dataset.

## Quantifying Qualitative Data for Regression Analysis

```{r modifying_data}
data$gender_int <- NA
data$gender_int[data$Gender. == "Male"] <- 0
data$gender_int[data$Gender. == "Female"] <- 1
#purpose: detecting the influence of gender on spending

data$occupation_int <- 0
data$occupation_int[data$X.Occupation == "Student + working"] <- 1
data$occupation_int[data$X.Occupation == "Student"] <- 1 
#purpose: detecting the influence of student status on spending

data$freq_int[data$Freq == "rarely (once two week/or a month)"] <- 0
data$freq_int[data$Freq == "Several times in a month"] <- 1
data$freq_int[data$Freq == "Several times a week"] <- 1
#purpose: detecting the influence of frequency at pubs on spending
```

## Regression Analysis

```{r regression}
model1 <- lm(WTS ~ Age. + Income. + gender_int + occupation_int + freq_int, data = data)
summary(model1)
```

From the regression model, we can see that age and income actually have no substantial effect on the Willingness to Spend variable y. We see that the gender, occupation, and frequency variables had strong negative influences on Willingness to Spend variable y. This was expected since I isolated students (who tend to have lower income or no income) in the occupation variable, isolated women (who tend to have a lower tolerance to alcohol then men meaning they would spend less at a pub) in the gender variable, and isolated respondents who go to pubs more often in the frequency variable.

## Conclusion

Overall, this dataset is not reliable enough to make a pronouncement about the usage of pubs in Armenia in general and another survey with a larger range of demographic characteristics would be needed. We have no location information besides the origin (data\$Stratum) of the participants of the survey. There also is an over-sampling of the young and low income as previously mentioned, and the times of the survey datapoints do not reflect a diverse range of times. Additionally, this data has not been vetted by peers on Kaggle and it cannot be certain what sampling methods were used to gather the data. Due to these flaws in the data and lack of clarity about collection methods, there are likely issues with the results of the regression model in the section above.
